---
title: "Exercise #6"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
author: "Jiyoun Seo(12558457)"
date: "`r Sys.Date()`"
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `exeRcise-sheet-3`. If you forgot how to do this, you can follow
    this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.


c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)
    
  strengths :
      - fast
      - good for collaboration
  weaknesses:
      - problems with binary/large files
      - it does not work automatically, so you need to use it actively.
    
e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.
    
    
    

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below: https://github.com/sandy3607/exeRcise-sheet-3
    
    
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
    
    
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.
    
    

## Exercise 3: Baby-Names in Munich (4.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2022` and
`2021`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>



a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.
    
```{r}
df2022 <- read.csv("open_data_portal_2022.csv")
df2021 <- read.csv("vornamen_2021.csv")
```
    

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

```{r}
typeof(df2021$Anzahl)
typeof(df2022$Anzahl)

# the types of the variable "Anzahl" is a character.
# the numbers are surrounded with ''.

df2021$Anzahl<-df2021$Anzahl %>%
  parse_number()

df2022$Anzahl<-df2022$Anzahl %>%
  parse_number()

typeof(df2021$Anzahl)
typeof(df2022$Anzahl)
# solution: the function parse_number dropped "'"s.
# repercussion : it turned the character-values into doubles.
```


c)  Calculate the total number of babies born in Munich in 2022
    and 2021. Which year had the bigger baby-boom?

```{r}
sum2021 <- sum(df2021$Anzahl) 
sum2022 <- sum(df2022$Anzahl)

sum2021
sum2022
```
There were more babies born in 2021.

d)  Add a new column `year` to both datasets which holds the correct
    year for each.
    
```{r}
df2021<-df2021%>%
  mutate(year = 2021)

df2022<-df2022%>%
  mutate(year = 2022)
```
    

e)  Combine both datasets into one using `bind_rows()`.

```{r}
df<-bind_rows(df2021, df2022)
```


f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.
```{r message=FALSE, warning=FALSE}
library(knitr)
```


```{r}
df1<-df%>%
  group_by(Vorname)%>%
  summarize(name_count = sum(Anzahl))%>%
  arrange(desc(name_count))
kable(head(df1, n=10), caption = "Top 10 Names in 2021 and 2022")
```
```{r}
df2<-df2021%>%
  group_by(Vorname)%>%
  summarize(name_count = sum(Anzahl))%>%
  arrange(desc(name_count))
kable(head(df2, n=10), caption = "Top 10 Names in 2021")
```

```{r}
df3<-df2022%>%
  group_by(Vorname)%>%
  summarize(name_count = sum(Anzahl))%>%
  arrange(desc(name_count))
kable(head(df3, n=10), caption = "Top 10 Names in 2022")
```


## Exercise 4: Chat GPT + apply (3 points)

For this task: Specifically use ChatGPT to solve the task and submit
your prompts in addition to the solution

a)  The code below does not work because the wrong apply function has
    been used. Find out which apply function would be correct and why it
    did not work. Correct the code. Also calculate the rowwise means.

###Create a sample data frame

tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )

running this makes this Error ;
Error: unexpected '\\' in "tax_data \"

```{r}
# tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
# 1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
# Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
# 3400) )
```
prompt: 

tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )
Please tell me what is wrong with this code and fix it.

Problem was: \ made a syntax error.

corrected code:

```{r}
tax_data <- data.frame(
  Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"),
  Tax_2019 = c(5000, 4000, 6000, 3500),
  Tax_2020 = c(4800, 4200, 5800, 3700),
  Tax_2021 = c(5200, 3800, 5900, 3400)
)

```


###Calculate column-wise means

running the given code made an Error;
Error: unexpected '\\' in "column_means \"

```{r}
# column_means \<- lapply(tax_data\[, -1\], 2, mean)
# 
# column_means
```


```{r}
# prompt:
# column_means \<- lapply(tax_data\[, -1\], 2, mean)
# 
# column_means
# 
# Please tell me what is wrong with this code and fix it.
```

Problem was:
\ caused a syntax error,and the second argument of lapply has to be a function and not a number like 2. To calculate the mean, use the mean function.

```{r}
column_means <- lapply(tax_data[, -1], mean)

column_means
```
is the right code.

Calculating the rowwise mean:
```{r}
row_means <- rowMeans(tax_data[, -1])

row_means
```


b)  Using ChatGPT try to understand what the rapply() function does.
    Create an easy example with mock data where the function is used and
    explain it in your words.

the function rapply() applies a function to elements of a list. (the list can have lists inside, too.) 

example:
```{r}
my_list <- list("hello", list("world", "yay"), list("fortstatsoft"))

result <- rapply(my_list, toupper, how = "replace")

print(result)
```
the rapply() function went through the list and applied the function toupper() to every elements in the list. The original values in the list were replaced by the new values.

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
